Enhancement of SDR in Thessaloniki

### 2024-05-21 GHI_enh_03_process.tex
Commit 2024-05-21 10:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-13}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-327.56 -157.11  -65.36  116.74  760.36

Coefficients:
                  Estimate Std. Error t value Pr(>|t|)    
(Intercept)      2.431e+02  4.880e+01   4.981  9.8e-07 ***
as.numeric(Date) 6.397e-08  3.907e-08   1.637    0.102    
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 210.1 on 363 degrees of freedom
Multiple R-squared:  0.007332,  Adjusted R-squared:  0.004597 
F-statistic: 2.681 on 1 and 363 DF,  p-value: 0.1024
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-327.56 -157.11  -65.36  116.74  760.36

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)       2.431e+02  4.880e+01   4.981  9.8e-07 ***
ST_E_monthly$Date 6.397e-08  3.907e-08   1.637    0.102    
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 210.1 on 363 degrees of freedom
Multiple R-squared:  0.007332,  Adjusted R-squared:  0.004597 
F-statistic: 2.681 on 1 and 363 DF,  p-value: 0.1024
\end{verbatim}

@@

\begin{verbatim}
aa
aatm
aday
AEin1
All_daily_ratio_lim
alpha
amean
ampl
asza
atype
avar
b
BIO_ELEVA
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
C4_test_cs_ref_ratio
C4_test_GLB_diff_THRES
C4_test_lowcut_ratio
C4_test_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
fit
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
lm_mean
lm_zeropoint
mean_BR_mean
mean_BR_median
mean_BR_min
mean_mean
mean_median
mean_min
mid
MIN_ELEVA
MIN_N
mm
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
slope_mean
slope_median
slope_min
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
t
tsy
units
variables_fl
xlim
yearstodo
ylim
zeropoint
zeropointA
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-05-13 09:11:34.5 athan@sagan GHI_enh_03_process.R 3.715344 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-20}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-319.48 -147.87  -56.18  101.04  719.45

Coefficients:
                  Estimate Std. Error t value Pr(>|t|)    
(Intercept)      1.379e+02  4.559e+01   3.025 0.002663 ** 
as.numeric(Date) 1.306e-07  3.650e-08   3.579 0.000391 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 196.3 on 363 degrees of freedom
Multiple R-squared:  0.03409,   Adjusted R-squared:  0.03143 
F-statistic: 12.81 on 1 and 363 DF,  p-value: 0.0003913
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-319.48 -147.87  -56.18  101.04  719.45

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)       1.379e+02  4.559e+01   3.025 0.002663 ** 
ST_E_monthly$Date 1.306e-07  3.650e-08   3.579 0.000391 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 196.3 on 363 degrees of freedom
Multiple R-squared:  0.03409,   Adjusted R-squared:  0.03143 
F-statistic: 12.81 on 1 and 363 DF,  p-value: 0.0003913
\end{verbatim}

@@

\begin{verbatim}
aa
aatm
aday
adjpoint55
AEin1
All_daily_ratio_lim
alpha
amean
ampl
asza
atype
avar
b
BIO_ELEVA
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
C4_test_cs_ref_ratio
C4_test_GLB_diff_THRES
C4_test_lowcut_ratio
C4_test_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
Energy_Div
fit
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
lm_mean
lm_zeropoint
mean_55
mean_BR_55
mean_BR_mean
mean_BR_median
mean_BR_min
mean_mean
mean_median
mean_min
mid
MIN_ELEVA
MIN_N
mm
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
slope_55
slope_mean
slope_median
slope_min
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
t
tsy
units
variables_fl
xlim
yearstodo
ylim
zeropoint
zeropointA
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-05-20 16:54:33.3 athan@tyler GHI_enh_03_process.R 6.553817 mins
\end{verbatim}

### 2024-05-21 GHI_enh_04_investigate.tex
Commit 2024-05-21 10:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-14}

@@

lmD: 0.80888 +/- 0.10628

lmY: 0.808883 +/- 0.106282

Arima: 0.809228 +/- 0.142401

@@

lmD: 0.002077 +/- 0.154863

lmY: 0.002083 +/- 0.154866

Arima: 0.069972 +/- 0.235505

@@

lmD: 0.0726 +/- 0.167744

lmY: 0.072609 +/- 0.167747

Arima: 0.141941 +/- 0.249338

@@

lmD: -0.087078 +/- 0.239888

lmY: -0.087089 +/- 0.239892

Arima: -0.087046 +/- 0.364497

@@

lmD: -0.191061 +/- 0.253235

lmY: -0.191072 +/- 0.253239

Arima: -0.191026 +/- 0.387751

@@

lmD: 0.442171 +/- 0.074674

lmY: 0.442172 +/- 0.074676

Arima: 0.442175 +/- 0.110249

@@

lmD: 0.506855 +/- 0.071215

lmY: 0.506856 +/- 0.071216

Arima: 0.50686 +/- 0.101481

@@

lmD: -1.191149 +/- 5.69247

lmY: -1.191222 +/- 5.692569

Arima: -1.138138 +/- 8.879593

@@

lmD: 0.00182 +/- 0.000272

lmY: 0.00182 +/- 0.000272

Arima: 0.001843 +/- 0.000361

@@

lmD: 0.000729 +/- 0.00028

lmY: 0.00073 +/- 0.00028

Arima: 0.000892 +/- 0.000462

@@

lmD: 0.000678 +/- 0.000314

lmY: 0.000678 +/- 0.000314

Arima: 0.000841 +/- 0.000507

@@

lmD: 0.001176 +/- 0.000309

lmY: 0.001176 +/- 0.000309

Arima: 0.001176 +/- 0.000483

@@

lmD: 0.001189 +/- 0.000301

lmY: 0.001189 +/- 0.000301

Arima: 0.001189 +/- 0.000463

@@

lmD: 0.001144 +/- 0.000235

lmY: 0.001144 +/- 0.000235

Arima: 0.001144 +/- 0.000366

@@

lmD: 0.0013 +/- 0.00023

lmY: 0.001301 +/- 0.00023

Arima: 0.001301 +/- 0.000342

@@

lmD: 0.376507 +/- 0.145413

lmY: 0.376518 +/- 0.145415

Arima: 0.436011 +/- 0.220423

@@

lmD: 0.319795 +/- 0.10019

lmY: 0.319795 +/- 0.100192

Arima: 0.3198 +/- 0.116665

@@

lmD: 0.10702 +/- 0.036516

lmY: 0.107021 +/- 0.036517

Arima: 0.107023 +/- 0.040195

@@

lmD: 0.108459 +/- 0.036231

lmY: 0.108461 +/- 0.036232

Arima: 0.108462 +/- 0.03848

@@

lmD: 0.144267 +/- 0.045486

lmY: 0.144265 +/- 0.045487

Arima: 0.144267 +/- 0.054102

@@

lmD: 0.022726 +/- 0.0184

lmY: 0.022726 +/- 0.0184

Arima: 0.022726 +/- 0.018993

@@

lmD: 0.018838 +/- 0.016889

lmY: 0.018838 +/- 0.016889

Arima: 0.018838 +/- 0.017339

@@

lmD: 0.194707 +/- 0.070475

lmY: 0.194706 +/- 0.070476

Arima: 0.194713 +/- 0.07858

@@

lmD: 0.227625 +/- 0.080608

lmY: 0.227625 +/- 0.080609

Arima: 0.22763 +/- 0.091764

@@

lmD: 0.447759 +/- 0.147315

lmY: 0.447759 +/- 0.147317

Arima: 0.447766 +/- 0.177904

@@

lmD: 0.000537 +/- 0.000135

lmY: 0.000537 +/- 0.000135

Arima: 0.000537 +/- 0.000157

@@

lmD: 0.000206 +/- 6e-05

lmY: 0.000206 +/- 6e-05

Arima: 0.000206 +/- 6.8e-05

@@

lmD: 0.000195 +/- 6.2e-05

lmY: 0.000195 +/- 6.2e-05

Arima: 0.000195 +/- 7e-05

@@

lmD: 4.8e-05 +/- 3.1e-05

lmY: 4.8e-05 +/- 3.1e-05

Arima: 4.8e-05 +/- 3.6e-05

@@

lmD: 3.7e-05 +/- 2.8e-05

lmY: 3.7e-05 +/- 2.8e-05

Arima: 3.7e-05 +/- 3.3e-05

@@

lmD: 0.000394 +/- 0.000106

lmY: 0.000394 +/- 0.000106

Arima: 0.000394 +/- 0.000122

@@

lmD: 0.00045 +/- 0.000117

lmY: 0.00045 +/- 0.000117

Arima: 0.00045 +/- 0.000135

@@

lmD: 0.011422 +/- 0.003629

lmY: 0.011422 +/- 0.003629

Arima: 0.011422 +/- 0.004188

@@

lmD: -1.014557 +/- 0.247144

lmY: -1.014539 +/- 0.247148

Arima: -1.025903 +/- 0.356761

@@

lmD: -1.13974 +/- 0.188386

lmY: -1.139735 +/- 0.188389

Arima: -1.172188 +/- 0.333189

@@

lmD: -1.100642 +/- 0.18719

lmY: -1.100638 +/- 0.187194

Arima: -1.133859 +/- 0.321558

@@

lmD: -1.242646 +/- 0.174098

lmY: -1.242654 +/- 0.174101

Arima: -1.284884 +/- 0.324863

@@

lmD: -1.259775 +/- 0.173629

lmY: -1.259783 +/- 0.173632

Arima: -1.301601 +/- 0.323343

@@

lmD: -1.034796 +/- 0.226955

lmY: -1.034779 +/- 0.226959

Arima: -1.050406 +/- 0.344658

@@

lmD: -1.02486 +/- 0.235592

lmY: -1.024843 +/- 0.235596

Arima: -1.038346 +/- 0.349707

@@

lmD: 0.138738 +/- 0.251457

lmY: 0.138759 +/- 0.251461

Arima: 0.138867 +/- 0.256234

@@

lmD: -0.001372 +/- 0.000292

lmY: -0.001372 +/- 0.000292

Arima: -0.001372 +/- 0.000322

@@

lmD: -0.001515 +/- 0.000226

lmY: -0.001515 +/- 0.000226

Arima: -0.001519 +/- 0.000269

@@

lmD: -0.001494 +/- 0.000234

lmY: -0.001494 +/- 0.000234

Arima: -0.001498 +/- 0.000275

@@

lmD: -0.001682 +/- 0.000209

lmY: -0.001683 +/- 0.000209

Arima: -0.00169 +/- 0.000262

@@

lmD: -0.001696 +/- 0.000208

lmY: -0.001696 +/- 0.000208

Arima: -0.001704 +/- 0.000262

@@

lmD: -0.001367 +/- 0.000272

lmY: -0.001367 +/- 0.000272

Arima: -0.001367 +/- 0.000304

@@

lmD: -0.001364 +/- 0.000281

lmY: -0.001364 +/- 0.000281

Arima: -0.001365 +/- 0.000312

@@

lmD: 0.002612 +/- 0.005505

lmY: 0.002612 +/- 0.005505

Arima: 0.002638 +/- 0.005739

@@

Arima: 0.107023 +/- 0.040196

@@

\begin{verbatim}
Warning: Removed 19 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 19 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 2 rows containing missing values or values outside the scale
range (`geom_tile()`).
\end{verbatim}

@@

lmY: 129.677 +/- 37.08333

@@

lmY: 48.08231 +/- 11.89152

@@

lmY: 0.080779 +/- 0.053347

@@

lmY: 0.065639 +/- 0.040043

@@

\begin{verbatim}
2024-05-14 07:45:19.2 athan@tyler GHI_enh_04_investigate.R 2.165741 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-20}

@@

lmD: 0.804776 +/- 0.104681

lmY: 0.804779 +/- 0.104683

Arima: 0.805121 +/- 0.139935

@@

lmD: 0.002645 +/- 0.154816

lmY: 0.002651 +/- 0.154818

Arima: 0.069946 +/- 0.23533

@@

lmD: 0.075523 +/- 0.167494

lmY: 0.075532 +/- 0.167497

Arima: 0.144037 +/- 0.248629

@@

lmD: -0.093964 +/- 0.240209

lmY: -0.093975 +/- 0.240213

Arima: -0.093932 +/- 0.364937

@@

lmD: -0.197599 +/- 0.2537

lmY: -0.197611 +/- 0.253704

Arima: -0.197564 +/- 0.388597

@@

lmD: 0.446578 +/- 0.074214

lmY: 0.446579 +/- 0.074216

Arima: 0.446582 +/- 0.10962

@@

lmD: 0.508145 +/- 0.070493

lmY: 0.508147 +/- 0.070494

Arima: 0.508152 +/- 0.100518

@@

lmD: -1.087297 +/- 5.707626

lmY: -1.087374 +/- 5.707725

Arima: -1.035804 +/- 8.936135

@@

lmD: 0.001815 +/- 0.00027

lmY: 0.001815 +/- 0.00027

Arima: 0.001839 +/- 0.000358

@@

lmD: 0.00073 +/- 0.000278

lmY: 0.00073 +/- 0.000278

Arima: 0.000891 +/- 0.000459

@@

lmD: 0.000679 +/- 0.000312

lmY: 0.000679 +/- 0.000312

Arima: 0.00084 +/- 0.000504

@@

lmD: 0.001171 +/- 0.000307

lmY: 0.001171 +/- 0.000307

Arima: 0.001171 +/- 0.000479

@@

lmD: 0.001184 +/- 0.000299

lmY: 0.001184 +/- 0.000299

Arima: 0.001184 +/- 0.00046

@@

lmD: 0.001143 +/- 0.000233

lmY: 0.001143 +/- 0.000233

Arima: 0.001143 +/- 0.000363

@@

lmD: 0.001299 +/- 0.000228

lmY: 0.001299 +/- 0.000228

Arima: 0.001299 +/- 0.00034

@@

lmD: 0.379481 +/- 0.144397

lmY: 0.379493 +/- 0.1444

Arima: 0.438045 +/- 0.218822

@@

lmD: 0.278784 +/- 0.099757

lmY: 0.278785 +/- 0.099759

Arima: 0.278791 +/- 0.11495

@@

lmD: 0.086758 +/- 0.036893

lmY: 0.086759 +/- 0.036894

Arima: 0.086761 +/- 0.03998

@@

lmD: 0.089859 +/- 0.036694

lmY: 0.089861 +/- 0.036694

Arima: 0.089862 +/- 0.038687

@@

lmD: 0.134313 +/- 0.043256

lmY: 0.134312 +/- 0.043256

Arima: 0.134314 +/- 0.05079

@@

lmD: 0.010492 +/- 0.018772

lmY: 0.010493 +/- 0.018773

Arima: 0.010494 +/- 0.019022

@@

lmD: 0.006132 +/- 0.017414

lmY: 0.006133 +/- 0.017414

Arima: 0.006133 +/- 0.017662

@@

lmD: 0.160601 +/- 0.070705

lmY: 0.160602 +/- 0.070706

Arima: 0.160604 +/- 0.07797

@@

lmD: 0.198524 +/- 0.080714

lmY: 0.198524 +/- 0.080715

Arima: 0.198532 +/- 0.091006

@@

lmD: 0.386176 +/- 0.138337

lmY: 0.386177 +/- 0.13834

Arima: 0.386184 +/- 0.16586

@@

lmD: 0.000476 +/- 0.000135

lmY: 0.000476 +/- 0.000135

Arima: 0.000476 +/- 0.000155

@@

lmD: 0.000172 +/- 6e-05

lmY: 0.000172 +/- 6e-05

Arima: 0.000172 +/- 6.8e-05

@@

lmD: 0.00016 +/- 6.3e-05

lmY: 0.00016 +/- 6.3e-05

Arima: 0.00016 +/- 7e-05

@@

lmD: 2.8e-05 +/- 3.2e-05

lmY: 2.8e-05 +/- 3.2e-05

Arima: 2.8e-05 +/- 3.6e-05

@@

lmD: 1.7e-05 +/- 2.9e-05

lmY: 1.7e-05 +/- 2.9e-05

Arima: 1.7e-05 +/- 3.3e-05

@@

lmD: 0.000347 +/- 0.000106

lmY: 0.000347 +/- 0.000106

Arima: 0.000347 +/- 0.000121

@@

lmD: 0.000402 +/- 0.000116

lmY: 0.000402 +/- 0.000116

Arima: 0.000402 +/- 0.000134

@@

lmD: 0.009848 +/- 0.003421

lmY: 0.009848 +/- 0.003422

Arima: 0.009849 +/- 0.003932

@@

lmD: -1.014326 +/- 0.242383

lmY: -1.01431 +/- 0.242387

Arima: -1.024849 +/- 0.345654

@@

lmD: -1.139227 +/- 0.182911

lmY: -1.139223 +/- 0.182914

Arima: -1.17037 +/- 0.320655

@@

lmD: -1.099532 +/- 0.181744

lmY: -1.09953 +/- 0.181747

Arima: -1.131269 +/- 0.309288

@@

lmD: -1.242636 +/- 0.168369

lmY: -1.242644 +/- 0.168371

Arima: -1.283474 +/- 0.312719

@@

lmD: -1.259539 +/- 0.167895

lmY: -1.259548 +/- 0.167897

Arima: -1.300028 +/- 0.311399

@@

lmD: -1.033796 +/- 0.221995

lmY: -1.03378 +/- 0.221999

Arima: -1.048334 +/- 0.332949

@@

lmD: -1.02427 +/- 0.230733

lmY: -1.024254 +/- 0.230737

Arima: -1.036798 +/- 0.338243

@@

lmD: 0.128338 +/- 0.244436

lmY: 0.128359 +/- 0.24444

Arima: 0.128462 +/- 0.249026

@@

lmD: -0.001358 +/- 0.00029

lmY: -0.001358 +/- 0.00029

Arima: -0.001358 +/- 0.00032

@@

lmD: -0.0015 +/- 0.000225

lmY: -0.0015 +/- 0.000225

Arima: -0.001504 +/- 0.000267

@@

lmD: -0.001479 +/- 0.000233

lmY: -0.001479 +/- 0.000233

Arima: -0.001483 +/- 0.000273

@@

lmD: -0.001666 +/- 0.000208

lmY: -0.001666 +/- 0.000208

Arima: -0.001674 +/- 0.00026

@@

lmD: -0.00168 +/- 0.000207

lmY: -0.00168 +/- 0.000207

Arima: -0.001688 +/- 0.00026

@@

lmD: -0.001352 +/- 0.00027

lmY: -0.001352 +/- 0.00027

Arima: -0.001353 +/- 0.000302

@@

lmD: -0.00135 +/- 0.000279

lmY: -0.00135 +/- 0.000279

Arima: -0.001351 +/- 0.00031

@@

lmD: 0.002398 +/- 0.005327

lmY: 0.002399 +/- 0.005328

Arima: 0.002424 +/- 0.005555

@@

Arima: 0.086761 +/- 0.03998

@@

\begin{verbatim}
Warning: Removed 16 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 16 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 1 row containing missing values or values outside the scale
range (`geom_tile()`).
\end{verbatim}

@@

lmY: 116.8672 +/- 33.89196

@@

lmY: 45.58799 +/- 10.96835

@@

lmY: 0.062157 +/- 0.054182

@@

lmY: 0.053059 +/- 0.041079

@@

\begin{verbatim}
2024-05-20 16:56:07.0 athan@tyler GHI_enh_04_investigate.R 1.334659 mins
\end{verbatim}
